---
title: "ML Assignment-1"
author: "Kowsick ram"
date: "2023-07-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Assignment - 1 - Exno: 09

1.	This exercise involves the Auto data set studied in the lab. Make sure that the missing values have been removed from the data.

#Removing Missing Data


```{r}
library(ISLR)
data(Auto)
Autodata=data.frame(Auto)
dim(Autodata)
#na.omit(Autodata)
```
```{r}
colMeans(is.na(Autodata))
```

```{r}

colnames(Autodata)
```
(a) Which of the predictors are quantitative, and which are qualitative?
```{r}
str(Autodata)
```


(b) What is the range of each quantitative predictor? You can answer this using the range() function. 

#Range of  Quantitative Predictor

```{r}
for (i in c(1,3,4,5,7)) {
  print(range(Autodata[,i]))
  
}
```
(c) What is the mean and standard deviation of each quantitative predictor? 

#Mean
```{r}
for(i in c(1,3,4,5,6,7)){
 print( mean(Autodata[,i]))
}
```
#Standard Deviation
```{r}
for(i in c(1,3,4,5,6,7)){
 print( sd(Autodata[,i]))
}
```
(d)	 Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains? 
```{r}
Sub_auto = Autodata[-(10:85),]
#Sub_auto
```

#Range
```{r}
for(i in c(1,3,4,5,6,7)){
 print( range(Sub_auto[,i]))
}
```

#Mean
```{r}
for(i in c(1,3,4,5,6,7)){
 print( mean(Sub_auto[,i]))
}

```
#Standard Deviation
```{r}
for(i in c(1,3,4,5,6,7)){
 print( sd(Sub_auto[,i]))
}
```
(e)	Using the full data set, investigate the predictors graphically, using scatterplots or other tools of your choice. Create some plots highlighting the relationships among the predictors. Comment on your findings.

```{r}
pairs(Autodata)
```
```{r}
plot(Autodata$mpg,Autodata$weight)
```
There Is a Negative correlation , that shows relationship that when there is increase in weight , there is decrease in miles.
```{r}
plot(Autodata$weight,Autodata$horsepower)
```
There Is a Positive Correlation , That shows a Relationship that, When there is Increase in Weight, There is Increase in Horsepower.

(f) Suppose that we wish to predict gas mileage (mpg) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting mpg? Justify your answer

Yes, from these graphs we can see some variables have positive, and some have negative, relationships to mpg outcome. mpg and horsepower have a negative relationship to one another (when horsepower increases, mpg decreases) while year and mpg have a positive relationship with each other (as year increases mpg also increases).
